Individual ABC reject Fits

### 2024-02-14 Model/abc_reject.qmd
plot posterior predictive densities; begin prep MAP predictions

---
title: Individual ABC Fits
author: Thomas Gorman
date: "`r Sys.Date()`"
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
---

@@

# organize test data predictions
post_dat <- nestSbjModelFit |> mutate(pp=furrr::future_pmap(list(id,Model,Fit_Method,data), ~{
   generate_data(..2, ..4 |> mutate(id=..1), ds, num_samples = 50, return_dat="test_data")
   })) |> 
  select(Fit_Method,pp,-data) |>  
  unnest(pp) |>  filter(expMode2=="Test") |> as.data.table()

@@

setorder(post_dat_avg, id, x, rank)
post_dat_l <- melt(post_dat_avg, id.vars = c("id", "condit", "Model", "Fit_Method", "x", "c", "lr", "rank","error"),
                   measure.vars = c("pred", "y"), variable.name = "Resp", value.name = "val")
post_dat_l[, Resp := fifelse(Resp == "y", "Observed",
                             fifelse(Model == "ALM", "ALM", "EXAM"))]
setorder(post_dat_l, id, Resp)
rm(post_dat_avg)

# organize training data predictions
pd_train <- nestSbjModelFit |> mutate(pp=furrr::future_pmap(list(id,Model,Fit_Method,data), ~{
   generate_data(..2, ..4 |> mutate(id=..1), ds, num_samples = 20, return_dat="train_data")
   })) |>
  select(Fit_Method,pp,-data) |>
  unnest(pp) |> as.data.table() |> filter(expMode2=="Train")

@@

@@

## Posterior Predictive: 
```{r, fig.width=12, fig.height=15}
#| eval: true
group_predictive_plots(post_dat_l) 
```

@@

@@

# post_tabs <- map(post_tabs, ~cbind(.x,run_info) |> mutate(fn=file_name))
post_tabs$agg_pred_full_train <- pt_train$agg_pred_full
post_tabs$block_pred_full <- pt_train$block_pred_full
post_tabs$block_pred_full_x <- pt_train$block_pred_full_x

@@

library(pander)
k = aov(dist~condit,data=testAvg)
pander::pandoc.table(summary(k), style="grid")

apaTables::apa.aov.table(k)

stats.table <- as.data.frame(summary(k)$coefficients)
rempsyc::nice_table(stats.table)

kable(summary(k))

summary(k)
pander::pander(summary(k))

>>>>

---
title: Individual ABC reject Fits
author: Thomas Gorman
date: "`r Sys.Date()`"
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
---

@@

# organize test data predictions
post_dat <- nestSbjModelFit |> mutate(pp=furrr::future_pmap(list(id,Model,Fit_Method,data), ~{
   generate_data(..2, ..4 |> mutate(id=..1), ds, num_samples = 20, return_dat="test_data")
   })) |> 
  select(Fit_Method,pp,-data) |>  
  unnest(pp) |>  filter(expMode2=="Test") |> as.data.table()

@@

setorder(post_dat_avg, id, x, rank)
post_dat_l <- melt(post_dat_avg, id.vars = c("id", "condit", "Model", "Fit_Method", "x", "c", "lr", "rank","error"),
                   measure.vars = c("pred", "y"), variable.name = "Resp", value.name = "val")
post_dat_l[, Resp := fifelse(Resp == "y", "Observed",
                             fifelse(Model == "ALM", "ALM", "EXAM"))]
setorder(post_dat_l, id, Resp)
#rm(post_dat_avg)

# organize training data predictions
pd_train <- nestSbjModelFit |> mutate(pp=furrr::future_pmap(list(id,Model,Fit_Method,data), ~{
   generate_data(..2, ..4 |> mutate(id=..1), ds, num_samples = 10, return_dat="train_data")
   })) |>
  select(Fit_Method,pp,-data) |>
  unnest(pp) |> as.data.table() |> filter(expMode2=="Train")

@@

theta_map <- post_dat_avg |> group_by(condit,Model,Fit_Method) |> summarize(c=median(c),lr=median(lr))

map <- simulation_function(sbj_data <- ds |> theta_map$c[1], , params$lr, input_layer = input_layer, 
                                    output_layer = output_layer, return_dat = return_dat)

@@

## Posterior Predictive: 
```{r, fig.width=12, fig.height=15}
#| eval: true
group_predictive_plots(post_dat_l)

testAvg |> ggplot(aes(x=vx)) + geom_density() + facet_wrap(~vb) +

post_dat_avg |> filter(rank==1) |> ggplot(aes(x=pred)) + geom_density() + facet_wrap(~x)

post_dat_avg |> filter(rank==1) |> ggplot(aes(x=pred)) + 
  geom_density() + geom_density(data=post_dat_avg, aes(x=y), color="red") +
  facet_wrap(condit~x,ncol=6)

post_dat_avg |> filter(Model=="EXAM",Fit_Method=="Test") |> ggplot(aes(x=pred)) + 
  geom_density() + geom_density(data=post_dat_avg, aes(x=y), color="red") +
  facet_wrap(condit~x,ncol=6)

post_dat_avg |> filter(Model=="ALM",Fit_Method=="Test") |> ggplot(aes(x=pred)) + 
  geom_density() + geom_density(data=post_dat_avg, aes(x=y), color="red") +
  facet_wrap(condit~x,ncol=6)

post_dat_avg |> filter(Fit_Method=="Test") |> ggplot(aes(x=pred)) + 
  geom_density(aes(fill=Model),alpha=.5) + geom_density(data=post_dat_avg, aes(x=y), color="black",alpha=2) +
  facet_wrap(condit~x,ncol=6)

post_dat_avg |> filter(Fit_Method=="Test_Train") |> ggplot(aes(x=pred)) + 
  geom_density(aes(fill=Model),alpha=.5) + geom_density(data=post_dat_avg, aes(x=y), color="black",alpha=2) +
  facet_wrap(condit~x,ncol=6)

post_dat_avg |> filter(Fit_Method=="Train",pred>0,pred<2000) |> ggplot(aes(x=pred)) + 
  geom_density(aes(fill=Model),alpha=.5) + geom_density(data=post_dat_avg, aes(x=y), color="black",alpha=2) +
  facet_wrap(condit~x,ncol=6)

@@

post_dat_avg |> group_by(id,condit,Fit_Method,x) |>
  ggplot(aes(x = x, y = error, fill=Model)) + 
  stat_bar + 
  facet_wrap(condit~Fit_Method, scales="free") + 
  labs(title = "Model Resituals - full posterior")

post_dat_avg |> group_by(id,condit,Fit_Method,x) |>
  filter(rank==1) |> 
  ggplot(aes(x = x, y = error, fill=Model)) + 
  stat_bar + 
  facet_wrap(condit~Fit_Method, scales="free") + 
  labs(title = "Model Residuals - best parameters")

@@

# post_tabs <- map(post_tabs, ~cbind(.x,run_info) |> mutate(fn=file_name))
# post_tabs$agg_pred_full_train <- pt_train$agg_pred_full
# post_tabs$block_pred_full <- pt_train$block_pred_full
# post_tabs$block_pred_full_x <- pt_train$block_pred_full_x

@@
